Comparing Machine Learning and Deep Learning Models with Attention Mechanisms for Multiple Authorship Attribution

### 2025-03-13 article.tex
ieee version started

The corresponding AST is structured as follows:
\begin{verbatim}
TranslationUnit
|--FunctionDefinition `int add(int a, int b) {`
   |--BasicTypeSpecifier `int`
   |--FunctionDeclarator `add(`
   |  |--IdentifierDeclarator `add`
   |  |--ParameterSuffix `(int a, int b)`
   |     |--ParameterDeclaration `int a`
   |     |  |--BasicTypeSpecifier `int`
   |     |  |--IdentifierDeclarator `a`
   |     |--ParameterDeclaration `int b`
   |        |--BasicTypeSpecifier `int`
   |        |--IdentifierDeclarator `b`
   |--CompoundStatement `{ return a + b; }`
      |--ReturnStatement `return a + b;`
         |--AddExpression `a + b`
            |--IdentifierName `a`
            |--IdentifierName `b`
\end{verbatim}
\label{verbatim:AST_example}

>>>>

The corresponding AST is structured as follows:
